Attribute fusion in a latent process model for time series of graphs

### 2011-04-20 ssp2011.tex
Add section on second order approximation

@@

properties. 

@@

\item For each time $t \in \mathbb{N}$ and vertex $i \in [n]$, there
  exists a matrix $\mathbf{Q}^{(i)}(t)$ such that for each $k,k' \in
  \mathscr{K}_{+}$

@@

    \label{eq:3}
    \mathbb{P}(W_{i}(t + \epsilon) = k' \, | \, W_{i}(t) = k)
    = \begin{cases}
      1 - \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) & \text{if $k
        = k'$} \\
      \mathbf{Q}_{kk}^{(i)}(t)\epsilon + o(\epsilon) &
      \text{otherwise}
    \end{cases}

@@

@@

\bibliography{ssp2011}
\end{document}

>>>>

\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

properties:

@@

\item For each $t \in \mathbb{N}$ and vertex $i \in [n]$, there exists
  a matrix $\mathbf{Q}^{(i)}(t)$ such that $W_i$, when restricted to
  the interval $[t, t+1)$, is a stationary, continuous-time Markov
  chain with state space $\mathscr{K}_+$, intensity matrix
  ${\mathbf{Q}^{(i)}(t)}$, and stationary distribution
  $\pi^{(i)}(t)$. $W$ is thus a stationary, continuous-time Markov chain with state
  space $\mathscr{K}_{+}^{n}$ and intentisy matrix
  $\otimes_{i=1}^{n}\mathbf{Q}^{(i)}(t)$.
\item There exists a $t^{*} \in \mathbb{N}$ and a $m < n$ such that 
  \item for  $t < t^{*}$
    \begin{gather*}
      \pi^{(i)}(t) \equiv \pi_0 \\
      Q^{(i)}(t) \equiv \mathbf{Q}_0
    \end{gather*}
  \item  for $t \geq t^{*}$
    \begin{gather*}
      \pi^{(1)}(t) = \dots = \pi^{(m)}(t) = \pi_1 \\
      \pi^{(m+1)}(t)  = \dots = \pi^{(n)}(t) = \pi_0 \\
      \mathbf{Q}^{(1)}(t)  = \dots = \mathbf{Q}^{(m)}(t) = \mathbf{Q}_1 \\
      \mathbf{Q}^{(m+1)}(t) = \dots = \mathbf{Q}^{(n)}(t) = \mathbf{Q}_0 
    \end{gather*}
The above properties characterize a random dot process model with a
change-point phenomena. We will refer to $(t^{*}, m, \pi_0, \pi_1,
\mathbf{Q}_0, \mathbf{Q}_1)$ as the change parameters. Because $W$ is completely
determined by the change parameters, we often choose to omit $W$ and
only mention $\mathscr{V}$ when referring to random dot process models
with change-point phenomena. For a rdpm $\mathscr{V}$ with change
parameters $(t^{*}, m, \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$, we can construct
several approximations to $\mathscr{V}$. Of particular interests are the
following two approximations.
\begin{definition}
  \label{def:1}
  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
  \pi_0, \pi_1, \mathbf{Q}_0, \mathbf{Q}_1)$. The first order approximation
  $\bar{\mathscr{V}}$ of $\mathscr{V}$ is the sequence $\{(\bar{X}(t),
  \bar{G}(t)\}_{t = 1}^{\infty}$ of independent random dot product
  spaces such that
 \item For $t < t^{*}$,

@@

     \label{eq:5}
     \bar{X}_{i}(t) \equiv \bar{\pi}_0.

@@

 \item For $t \geq t^{*}$
   \begin{gather*}
     \bar{X}_{i}(t) \equiv \bar{\pi}_1 \quad \text{for $i \leq m$} \\
     \bar{X}_{i}(t) \equiv \bar{\pi}_0 \quad \text{for $i > m$} 
   \end{gather*}

@@

 where $\bar{\pi}_0$ and $\bar{\pi}_1$ are sub-probability vectors
 obtained by removing the last coordinate of $\pi_0$ and $\pi_1$. 
\end{definition}
\begin{definition}
  \label{def:2}
  Let $\mathscr{V}$ be a rdpm with change parameters $(t^{*}, m,
  \pi_0, \pi_1, Q_0, Q_1)$. Define $\mathbf{Z}_0$ and $\mathbf{Z}_1$
  by
  \begin{gather}
    \mathbf{Z}_0 = (\mathbf{1}\mathbf{\pi}_0^{T} -
    \mathbf{Q}_0)^{-1}(\mathbf{I} - \mathbf{1}\pi_0^{T}) \\
    \mathbf{Z}_1 = (\mathbf{1}\mathbf{\pi}_1^{T} -
    \mathbf{Q}_1)^{-1}(\mathbf{I} - \mathbf{1}\pi_1^{T})
  \end{gather}
  $\mathbf{Z}_0$ and $\mathbf{Z}_1$ are the fundamental matrices
  for the continuous-time Markov chain on $\mathscr{K}$ with intensity
  matrix $\mathbf{Q}_0$ and $\mathbf{Q}_1$ (see
  e.g., \cite[p. 55]{asmussen03:_applied_probab_queues}). Let
  $\Sigma_0$ and $\Sigma_1$ be given by
  \begin{gather*}
    \Sigma_0 = \mathrm{diag}(\pi_0) \mathbf{Z}_0 + \mathbf{Z}_0^{T}
    \mathrm{diag}(\pi_0) \\
    \Sigma_1 = \mathrm{diag}(\pi_1) \mathbf{Z}_1 + \mathbf{Z}_1^{T}
    \mathrm{diag}(\pi_1)
  \end{gather*}
  A second order approximation $\hat{\mathscr{V}}$ of $\mathscr{V}$
  is the sequence $\{\hat{X}(t), \hat{G}(t)\}_{t=1}^{\infty}$ where
  \item For each $t$ and each $i \in [n]$, $\hat{X}^{i}(t)$ is a
    random vector obtained by truncating a multivariate normal random
    vector $Z_{i}(t)$ to $\mathscr{S}$.
  \item For $t < t^{*}$,
    \begin{gather}
      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0 \\
      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma^{0}}
    \end{gather}
  \item For $t \geq t^{*}$,  
    \begin{gather*}
      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_0, \quad \text{for $i \leq
        m$}  \\
      \mathbb{E}[Z_i(t)] \equiv \bar{\pi}_1, \quad \text{for $i > 
        m$}  \\
      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{0} \quad \text{for $i
        \leq m$} \\
      \mathrm{Var}[Z_i(t)] \equiv \hat{\Sigma}_{1} \quad \text{for $i
        > m$}
    \end{gather*}
    where $\hat{\Sigma}_0$ and $\hat{\Sigma}_1$ are the matrices
    obtained by removing last row and column of $\Sigma_0$ and
    $\Sigma_1$. 
\end{definition}
\bibliography{ssp2011}
\end{document}
